%---------------------------------------------------
% Nombre: bibliografia.tex  
% 
% Bibliografia
%---------------------------------------------------

\begin{thebibliography}{99}


\bibitem{moa}
	\emph{} Albert Bifet, Geoff Holmes, Richard Kirkby, Bernhard Pfahringer (2010); MOA: Massive Online Analysis; \textit{Journal of Machine Learning Research} 11: 1601-1604 

\bibitem{moa2}
	\emph{} Moa Web Site \url{https://moa.cms.waikato.ac.nz}





\bibitem{cd1}
	\emph{}Sunanda Gamage and Upeka Premaratne. 2017. Detecting and Adapting to Concept Drift in Continually Evolving Stochastic Processes. \textit{Proceedings of the International Conference on Big Data and Internet of Thing (BDIOT2017)}. ACM, New York, NY, USA, 109-114
	
\bibitem{cd2}
	\emph{}Sylvio Barbon Junior, Gabriel Marques Tavares, Victor G. Turrisi da Costa, Paolo Ceravolo, and Ernesto Damiani. 2018. A Framework for Human-in-the-loop Monitoring of Concept-drift Detection in Event Log Stream. \textit{Companion of the The Web Conference 2018 on The Web Conference 2018 (WWW '18)}. International World Wide Web Conferences Steering Committee, Republic and Canton of Geneva, Switzerland, 319-326.

\bibitem{cd3}
	\emph{}Sun, Y., Wang, Z., Bai, Y., \& Dai, H. A Classifier Graph based Recurring Concept Detection and Prediction Approach.
	
\bibitem{cd4}
	\emph{}Wang, Z., Tian, M., \& Jia, C. (2017, December). An Active and Dynamic Botnet Detection Approach to Track Hidden Concept Drift. In \textit{International Conference on Information and Communications Security} (pp. 646-660). Springer, Cham.
	
\bibitem{CVFDT}
	\emph{}Hulten, G., Spencer, L., \& Domingos, P. (2001, August). Mining time-changing data streams. In \textit{Proceedings of the seventh ACM SIGKDD international conference on Knowledge discovery and data mining} (pp. 97-106). ACM.	
	
\bibitem{street}
	\emph{}Street, W. N., \& Kim, Y. (2001, August). A streaming ensemble algorithm (SEA) for large-scale classification. In \textit{Proceedings of the seventh ACM SIGKDD international conference on Knowledge discovery and data mining} (pp. 377-382). ACM.	
	
	
\bibitem{wang}
	\emph{}Wang, H., Fan, W., Yu, P. S., \& Han, J. (2003, August). Mining concept-drifting data streams using ensemble classifiers. In \textit{Proceedings of the ninth ACM SIGKDD international conference on Knowledge discovery and data mining} (pp. 226-235). AcM.	
		
	
\end{thebibliography}
%---------------------------------------------------